---
title: "Berlin"
output: html_document
date: "2024-05-03"
---

```{r}
library(spdep)
library(elevatr)
library(sf)
library(spData)
library(tidyverse)
library(ggplot2)
library(leaflet)
library(terra)
library(lmtest)
library(giscoR)
library(ggmap)
library(mapview)
library(tmap)
library(spatialreg)
library(hglm)
library(plot.matrix)
library(viridis)
library(mapsf)
```


```{r}
#Combining Weekdays and Weekends Datasets for berlin into a single dataframe
berlin <- read.csv("~/GitHub/AirBnb-Spatial-project/data sets/berlin_weekdays.csv")

str(berlin)
```



```{r, results='asis'}
# Load the gt package
library(gt)

# Creating data frame to store the summary statistics
summary_df <- data.frame(
  Variable = names(berlin)[-c(1:7)],  
  Minimum = sapply(berlin[, -c(1:7)], min),  
  Q1 = sapply(berlin[, -c(1:7)], quantile, probs = 0.25),  
  Median = sapply(berlin[, -c(1:7)], median),  
  Mean = sapply(berlin[, -c(1:7)], mean),  
  Q3 = sapply(berlin[, -c(1:7)], quantile, probs = 0.75),
  Maximum = sapply(berlin[, -c(1:7)], max) 
)

# Creating a gt table
summary_table <- gt(summary_df) %>%
  tab_spanner(label = "Summary Statistics") %>%
  tab_header(
    title = "Summary Statistics",
    subtitle = "Table displaying summary statistics for Berlin dataset"
  )

# Print the summary table
summary_table
```


```{r}
# Visualize data distributions of key values: realSum, cleanliness_rating, guest_satisfaction_overall, dist, and metro_dist
par(mfrow = c(3, 2))  # Set up a 3x2 grid for plots
# Histograms
hist(berlin$realSum, main = "Distribution of Total Price", xlab = "Total Price (realSum)", col = "pink")
hist(berlin$cleanliness_rating, main = "Distribution of Cleanliness Rating", xlab = "Cleanliness Rating", col = "lightgreen")
hist(berlin$guest_satisfaction_overall, main = "Distribution of Guest Satisfaction", xlab = "Overall Guest Satisfaction", col = "salmon")
hist(berlin$dist, main = "Distribution of Distance from City Center", xlab = "Distance (km)", col = "lightyellow")
hist(berlin$metro_dist, main = "Distribution of Distance from Metro", xlab = "Distance (km)", col = "lavender")
```



```{r}
# Box plots
boxplot(berlin$realSum, main = "Box Plot of Total Price", col = "pink")
# Box plot for cleanliness rating
boxplot(berlin$cleanliness_rating, main = "Box Plot of Cleanliness Rating", col = "lightgreen")
# Box plot for guest satisfaction overall
boxplot(berlin$guest_satisfaction_overall, main = "Box Plot of Guest Satisfaction Overall", col = "salmon")
# Box plot for distance from city center
boxplot(berlin$dist, main = "Box Plot of Distance from City Center", col = "lightyellow")
# Box plot for distance from metro station
boxplot(berlin$metro_dist, main = "Box Plot of Distance from Metro Station", col = "lavender")
```

```{r}
#Creating geomtetry points

bar_sf <- st_as_sf(berlin, coords = c("lng", "lat"), crs = 4326)
st_geometry(bar_sf)
st_crs(bar_sf)
```


```{r}
# Evelation points
bar_sf |>  get_elev_raster(z = 7,
                           clip = "locations", neg_to_na = TRUE) |> 
  rast() -> bar_elev
```


```{r}
#Creating neighbouring o
(bar_sf|> knearneigh(k=10) |>
 knn2nb(row.names=bar_sf$...1, sym = TRUE) -> bar_nb)
bar_nb |> nb2lines(coords=st_geometry(bar_sf)
 ) -> bar_nb_sf
```

```{r}

#visualisation
mapview(bar_sf) + mapview(bar_nb_sf, color="red4")
mapview(bar_sf, zcol="guest_satisfaction_overall")
```


```{r}
# LEAFLET MAP for visualisation
library(leaflet)
leaflet(data = berlin) %>%
  addTiles() %>%
  addCircleMarkers(
    lng = ~lng,  # Longitude
    lat = ~lat,  # Latitude
    radius = 3,  # Adjust the size of the dots as needed
    color = "salmon",  # Color of the dots
    fillOpacity = 0.7,  # Opacity of the dots
    popup = ~paste("Guest Satisfaction Overall:", guest_satisfaction_overall)
  ) %>%
  addLegend("bottomright", 
            colors = "salmon", 
            labels = "Guest Satisfaction Overall",
            opacity = 0.7)
```


```{r}
# Spatial weights matrix using distance-based criterion
unb <- knn2nb(knearneigh(bar_sf, k = 5))
lw <- nb2listw(unb, style = "W")

moran <- moran.test(bar_sf$guest_satisfaction_overall, listw = lw, randomisation = TRUE, alternative = "two.sided")
moran

lm_null <- lm(guest_satisfaction_overall ~ 1, data = bar_sf)
moran.test(residuals(lm_null), listw = lw, randomisation = FALSE, alternative = "two.sided")

form_pre <- bar_sf$guest_satisfaction_overall ~ log(bar_sf$realSum) + bar_sf$host_is_superhost + bar_sf$attr_index + bar_sf$person_capacity + bar_sf$dist + bar_sf$metro_dist
lm_obj_pre <- lm(form_pre, data = bar_sf)
moran.test(residuals(lm_obj_pre), listw = lw, randomisation = FALSE, alternative = "two.sided")

lm.RStests(lm_obj_pre, listw = lw, test = "all")

# Create symmetric spatial weights
unb <- knn2nb(knearneigh(bar_sf, k = 5), sym = TRUE)
lwB <- nb2listw(unb, style = "B")
# Fit the CAR model with symmetric weights
car1 <- spautolm(form_pre, data = bar_nb_sf, listw = lwB, family = "CAR")
summary(car1, Nagelkerke = TRUE)
```

```{r}
bar_sf$ranef_ml <- car1$fit$signal_stochastic
W <- as(lwB, "CsparseMatrix")
car2 <- hglm(fixed=form_pre, random= ~ 1|X, data=bar_sf, family = gaussian(), rand.family=CAR(D=W))
car2
```

```{r}
sar1B <- spautolm(form_pre, data = bar_sf, listw = lwB, family = "SAR")
summary(sar1B, Nagelkerke = TRUE)

lw <- nb2listw(unb, style = "W")
e <- eigenw(lw)
sar1 <- spautolm(form_pre, data = bar_sf, listw = lw, family = "SAR", control = list(pre_eig = e))
summary(sar1, Nagelkerke = TRUE)

form_pre <- bar_sf$guest_satisfaction_overall ~ log(bar_sf$realSum) + bar_sf$host_is_superhost + bar_sf$attr_index + bar_sf$person_capacity + bar_sf$dist + bar_sf$metro_dist

SEM_pre <- errorsarlm(form_pre, data = bar_sf, listw = lw, control = list(pre_eig = e))
summary(SEM_pre, Nagelkerke = TRUE)

```
```

```{r}
GNM_pre <- sacsarlm(form_pre, data=bar_sf, listw=lw, Durbin=update(form_pre, ~ . - Metrop), control=list(pre_eig1=e, pre_eig2=e))
SAC_pre <- sacsarlm(form_pre, data=bar_sf, listw=lw, control=list(pre_eig1=e, pre_eig2=e))
SDEM_pre <- errorsarlm(form_pre, data=bar_sf, listw=lw, Durbin=update(form_pre, ~ . - Metrop), control=list(pre_eig=e))
SDM_pre <- lagsarlm(form_pre, data=bar_sf, listw=lw, Durbin=update(form_pre, ~ . - Metrop), control=list(pre_eig=e))
SLM_pre <- lagsarlm(form_pre, data=bar_sf, listw=lw, control=list(pre_eig=e))
SLX_pre <- lmSLX(form_pre, data=bar_sf, listw=lw, Durbin=update(form_pre, ~ . - Metrop))
OLS_pre <- lm(form_pre, data=bar_sf)
```

```{r}
mlist_pre <- list(GNM=GNM_pre, SAC=SAC_pre, SDEM=SDEM_pre, SDM=SDM_pre, SLX=SLX_pre, SEM=SEM_pre, SLM=SLM_pre, OLS=OLS_pre)
m <- length(mlist_pre)
LR_pre <- matrix(NA, ncol=m, nrow=m)
colnames(LR_pre) <- rownames(LR_pre) <- names(mlist_pre)
for (j in 2:m) LR_pre[1, j] <- lrtest(mlist_pre[[1]],
                                      mlist_pre[[j]])[[2, "Pr(>Chisq)"]]
for (j in 6:8) LR_pre[2, j] <- lrtest(mlist_pre[[2]],
                                      mlist_pre[[j]])[[2, "Pr(>Chisq)"]]
for (j in c(5, 6, 8)) LR_pre[3, j] <- lrtest(mlist_pre[[3]],
                                             mlist_pre[[j]])[[2, "Pr(>Chisq)"]]
for (j in c(5:8)) LR_pre[4, j] <- lrtest(mlist_pre[[4]],
                                         mlist_pre[[j]])[[2, "Pr(>Chisq)"]]
for (i in 5:7) LR_pre[i, 8] <- lrtest(mlist_pre[[i]],
                                      mlist_pre[[8]])[[2, "Pr(>Chisq)"]]
```


```{r}
opar <- par(mar=c(3.1, 3.1, 3.1, 7.1), cex.axis=0.8)
plot(LR_pre, breaks=c(0, 10^-(8:0)), col=viridis, las=1)


## Bayesian Estimation
SAC_pre_maj <- sacsarlm(form_pre, data=bar_sf, listw=lw, control=list(pre_eig1=e, pre_eig2=e), llprof=40)
SAC_track <- capture.output(sac <- sacsarlm(form_pre, data=bar_sf, listw=lw, control=list(pre_eig1=e, pre_eig2=e), quiet=FALSE))
c(SAC_pre_maj$rho, SAC_pre_maj$lambda)
```


```{r}
c(SAC_pre_maj$rho/SAC_pre_maj$rho.se, SAC_pre_maj$lambda/SAC_pre_maj$lambda.se)
```

```{r}
m <- -matrix(SAC_pre_maj$llprof$ll, 40, 40)
con <- textConnection(SAC_track)
sac_track <- read.table(con, skip=14)
close(con)
contour(SAC_pre_maj$llprof$xseq, SAC_pre_maj$llprof$yseq, m, levels=quantile(c(m), seq(0,1,0.1)), xlab="rho", ylab="lambda", col="blue4")
abline(h=SAC_pre_maj$rho, v=SAC_pre_maj$lambda, lwd=3, col="lightgreen")
lines(sac_track$V2, sac_track$V4, col="darkred")
```

## bayesian estimation
```{r}
set.seed(12345)
SAC_bayes <- spBreg_sac(form_pre, data=bar_sf, listw=lw, control=list(ndraw=20000L, nomit=2000L))
```

```{r}
summary(SAC_bayes[, c("rho", "lambda", "sige")])
```

```{r}
opar <- par(mfrow=c(2, 1)) 
plot(SAC_bayes[, c("rho", "lambda", "sige")], smooth=TRUE)
```
##3 GMM estimation  
```{r}
library(spatialreg)
SAC_gmm <- lagsarlm(form_pre, data = bar_sf, listw = lw)
# Extracting coefficients and s2
c(coef(SAC_gmm)[c("lambda", "rho")], s2 = SAC_gmm$s2)
```
